---
title: "Lab10"
author: "Ruixuan Hu"
date: "11/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



1. Write a function that generates numbers from binomial(n, p) distribution using runif() function. Hint: binomial(n, p) random variable can be defined as a sum of n independent Bernoulli(p) random variables.

```{r}
count = 0 
binfunc <- function(size,n,p) {
  
  for (i in 1:size) { 
    for (i in 1:n) {
      a[i] <- runif(1)
      if (a[i] <= p)
        a[i] = 0
      else 
        a[i] = 1
    count = count + a[i]
    }
    return(count)
  }
  
}

binfunc(25,10,0.4)
```



2. Compare performance of your function with rbinom() using microbenchmark() function. 

```{r}
microbenchmark(rbinom(25,10,0.4),binfunc(25,10,0.4))
```


3. Suppose we want to simulate data from a linear regression model:
Yi =β0 +β1 ×Xi +εi i=1,...,N
where ε ∼ N(0,3) and X is a covariate that ranges between 20 and 40. Let β0 = 15 and β1 = 0.4 are known coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function for reproducibility.


First, get the coefficients.
```{r}
β0 <- 15
β1 <- 4

set.seed(321)
results <- matrix(nrow = 50, ncol = 2)
for (i in 1:50) {
  x1 <- runif(100)
  e <- rnorm(100, mean = 0, sd = 3)
  y1 <- β0+β1*x1+e
  
  linereg<- lm(y1 ~ x1)
  results[i,] <- coef(y)
  
}

ggplot(data = linereg, aes(x = linereg$residuals,y=linereg$fitted.values)) +
geom_point() +
geom_abline()
```





4. Box-Muller algorithm: generate U1 and U2 two independent uniform(0, 1) random variables and set: R =  −2 log(U1) and θ = 2πU2
then
X = Rcos(θ) and Y = Rsin(θ)
are two independent normal variables. Write a function that generates normal variates using Box-Muller algorithm. Compare simulated data from your function with simulated data from rnorm() function using ggplot() (histogram?).


First, generate the data.
```{r}
Myfunc <- function(n){
set.seed(1234)
U1 <- runif(n)
U2 <- runif(n)
R <- sqrt((-2) * log(U1))
sigma <- (2 * pi * U2)
X <- R * cos(sigma)


return(X)
}


```

Then use histogram for comparation,
```{r}
dataBM <- Myfunc(1000)
datarnorm <- rnorm(1000,mean=0,sd=1)

hist(dataBM)
hist(datarnorm)
```

